---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# compBiplot

<!-- badges: start -->
<!-- badges: end -->

The goal of compBiplot is to provide tools for constructing log-ratio biplots for compositional datasets. The package implements centered and isometric log-ratio transformations (clr and ilr), and generates covariance- or correlation-based biplots via log-ratio PCA (LR-PCA).

## Installation

You can install the development version of **compBiplot** from GitHub:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ZhilongZ2/compBiplot")
library(compBiplot)

```

## Example

Here are some basic examples which show you how to use **compBiplot**:

```{r example}
library(compBiplot)
## basic example code

# The package includes the cleaned Ecuador–Mexico blood panel:
data("ECU.MF")
head(ECU.MF)

# ?ECU.MF
# See ‘data-raw/ECU_MF.R’ for full preprocessing code.
```

**compBiplot** also includes two common log-ratio transformations that deal with compositional data. They are implemented to be able to handle zero entries:
```{r}
# Extract the five compositional parts

X <- as.matrix(ECU.MF[, c("neutrophils", "lymphocytes",
"monocytes", "eosinophils", "basophils")])

clr_X <- clr_transform(X, zero.method = "cmultRepl")
head(clr_X)

ilr_X <- ilr_transform(X, zero.method = "cmultRepl")
head(ilr_X)
```

Remaining *TODOS* for compBiplot:  
* Add R functions: corrbiplot, covbiplot  
* Add tests and examples  
* Add vignettes    
* Refine documents 

