---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# compBiplot

<!-- badges: start -->
<!-- badges: end -->

The goal of compBiplot is to provide tools for constructing log-ratio biplots for compositional datasets. The package implements centered and isometric log-ratio transformations (clr and ilr), and generates covariance- or correlation-based biplots via log-ratio PCA (LR-PCA).

## Installation

You can install the development version from GitHub:

```r
# install.packages("devtools")
devtools::install_github("ZhilongZ2/compBiplot")
library(compBiplot)


## Installation

You can install the development version of compBiplot from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("ZhilongZ2/compBiplot")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(compBiplot)
## basic example code

# Find the sources of dataset included by
# ?ECU.MF
```

Remaining TODOS for compBiplot:
* Add R functions: ilr, corrbiplot, covbiplot  
* Add tests  
* Add vignettes  
* Refine documents  

